TA data filtration: despike()

### 2019-11-26 TA_filter_despike.Rmd
script update with final results for TA_filter_despike

Here the TA dataset already cleaned by despike() at the end of the ny-alesund_cc.R script. If we zoom in November 2019 we can see the drop in data around midnight each day, due to acid washing cycle.

@@

## Despike() parameters settings
The idea was to find best parameters (n and k) in despike() in order to keep largest data (N = number of points) with a smallest standard deviation (V).

  - Create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and 25 - 221 for k.

@@

Number of point > 80% and sd < 80 were choosen here.

@@

```{r despike parameters, echo=FALSE, warning=FALSE, message=FALSE}

tmp <- NULL
#create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and 25 - 221 for k.
df <- expand.grid(n = seq(0.1, 1, length.out =0.1 ), k =as.integer(seq(25, 221, by = 4)))
df$N <- NULL
# create a tmp vector with different n, k parameters when i is different. i corresponds to the different lines of df and thus has different combinaisons of n,k.
for (i in 1:
     nrow(df)) {
  tmp <- despike(d_hour$AT_filtered, reference= "median", n=df$n[i], k=df$k[i], replace="NA")
  #create a new N column with the number of data. 
  df$N[i] <- length(tmp[!is.na(tmp)])
  #create a new V column with the standard deviation of each despike measurement.
  df$V[i] <- sd(tmp, na.rm = TRUE)
  }
summary(df)

#We want to keep data with highest N and smallest V
# We transform N in percentage for easy understanding.
df$percentN <- (df$N/max(df$N))*100

@@

Best n and k were found for 0.2 > n < 0.3 and 109 >= K <= 221
```{r final plot, echo=FALSE, warning=FALSE, message=FALSE}
# final plot
at_fb_xts <- dplyr::select(d_hour, datetime,AT_filtered)
at_fb_xts <- as.xts(at_fb_xts, order.by = at_fb_xts$datetime)
dygraph(at_fb_xts, ylab="at") %>%
  dySeries("AT_filtered", color = "blue", strokeWidth = 0, label = "raw") %>%
  #dySeries("AT_filtered2", color = "red", strokeWidth = 0, label = "filt") %>%
  #dySeries("AT_filtered3", color = "green", strokeWidth = 0, label = "filt3") %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.2,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
  dyRangeSelector(height = 30)
```

>>>>

TA dataset (blue) already cleaned by despike() with n = 0.5 and k = 121, at the end of the ny-alesund_cc.R script. If we zoom in November 2019 we can see lot of drops in data around midnight each day, due to acid washing cycle.

@@

## Despike() parameters settings
The idea was to find better parameters (n and k) in despike() in order to keep largest data (N = number of points) with a smallest standard deviation (V).

  - Create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and between 25 - 221 for k.

@@

@@

Summary of dataframe with all posibilities + N and V plots:

```{r despike parameters, echo=FALSE, warning=FALSE, message=FALSE}
tmp <- NULL
#create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and 25 - 221 for k.
df <- expand.grid(n = seq(0.1, 1, by =0.1 ), k =as.integer(seq(25, 221, by = 4)))
df$N <- NULL
# create a tmp vector with different n, k parameters when i is different. i corresponds to the different lines of df and thus has different combinaisons of n,k.
for (i in 1:
     nrow(df)) {
  tmp <- despike(d_hour$AT_filtered, reference= "median", n=df$n[i], k=df$k[i], replace="NA")
  #create a new N column with the number of data. 
  df$N[i] <- length(tmp[!is.na(tmp)])
  #create a new V column with the standard deviation of each despike measurement.
  df$V[i] <- sd(tmp, na.rm = TRUE)
  }
summary(df)

@@

Here, best dataframe compiling best n and k resulting of Number of point (N) > 80% and sd (V) < 80:
- 0.2 > n < 0.3 
- 109 > k < 221

```{r best despike parameters, echo=FALSE, warning=FALSE, message=FALSE}
#We want to keep data with highest N and smallest V
# We transform N in percentage for easy understanding.
df$percentN <- (df$N/max(df$N))*100

# despike
d_hour <- d_hour %>%
  dplyr::mutate(AT_filtered2= despike(d_hour$AT_filtered, reference= "median", n=0.3, k=217, replace="NA"))
d_hour <- d_hour %>%
  dplyr::mutate(AT_filtered3= despike(d_hour$AT_filtered2, reference= "median", n=0.3, k=217, replace="NA"))
#dplyr::mutate(AT_filtered2= despike(d_hour$AT_filtered, reference= "median", n=0.3, k=217, replace="NA"))
```

In the following plot, n = 0.3 and k = 217 were kept as 2nd time despike() parameters (red dots). A third despike() run (green dots) was discarded because of the large lack of data.

```{r final plot, echo=FALSE, warning=FALSE, message=FALSE}
# final plot
at_fb_xts <- dplyr::select(d_hour, datetime,AT_filtered,AT_filtered2, AT_filtered3)
at_fb_xts <- as.xts(at_fb_xts, order.by = at_fb_xts$datetime)
dygraph(at_fb_xts, ylab="at") %>%
  dySeries("AT_filtered", color = "blue", strokeWidth = 0, label = "raw") %>%
  dySeries("AT_filtered2", color = "red", strokeWidth = 0, label = "filt") %>%
  dySeries("AT_filtered3", color = "green", strokeWidth = 0, label = "filt3") %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.2,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
  dyRangeSelector(height = 30)
```
